
%All Mode 3.

\subsubsection{Sunday}

\psalm{118 a}


\gregorioscore{gabc/118.1-3b}

\setcounter{versecount}{2}

\latin{Beáti, qui scrutántur testi\textbf{mó}nia \textbf{e}jus:~* in toto corde exquí\textit{runt} \textbf{e}um.}\vern{Blessed are they who search his testimonies: that seek him with their whole heart.}

\latin{Non enim qui operántur i\textbf{ni}qui\textbf{tá}tem,~* in viis ejus ambu\textit{la}\textbf{vé}runt.}\vern{For they that work iniquity, have not walked in his ways.}

\latin{\textbf{Tu} man\textbf{dá}sti~* mandáta tua custodí\textit{ri} \textbf{ni}mis.}\vern{Thou hast commanded thy commandments to be kept most diligently.}

\latin{Utinam dirigántur \textbf{vi}æ \textbf{me}æ,~* ad custodiéndas justificatió\textit{nes} \textbf{tu}as!}\vern{O! that my ways may be directed to keep thy justifications.}

\latin{Tunc \textbf{non} con\textbf{fún}dar,~* cum perspéxero in ómnibus mandá\textit{tis} \textbf{tu}is.}\vern{Then shall I not be confounded, when I shall look into all thy commandments.}

\latin{Confitébor tibi in directi\textbf{ó}ne \textbf{cor}dis:~* in eo quod dídici judícia justíti\textit{æ} \textbf{tu}æ.}\vern{I will praise thee with uprightness of heart, when I shall have learned the judgments of thy justice.}

\latin{Justificatiónes \textbf{tu}as cu\textbf{stó}\textbf{di}am:~* non me derelínquas us\textit{que}\textbf{quá}que.}\vern{I will keep thy justifications: O! do not thou utterly forsake me.}

\latin{In quo córrigit adolescéntior \textbf{vi}am \textbf{su}am?~* in custodiéndo sermó\textit{nes} \textbf{tu}os.}\vern{By what doth a young man correct his way? by observing thy words.}

\latin{In toto corde meo \textbf{ex}qui\textbf{sí}\textbf{vi} te:~* ne repéllas me a mandá\textit{tis} \textbf{tu}is.}\vern{With my whole heart have I sought after thee: let me not stray from thy commandments.}

\latin{In corde meo abscóndi e\textbf{ló}quia \textbf{tu}a:~* ut non pec\textit{cem} \textbf{ti}bi.}\vern{Thy words have I hidden in my heart, that I may not sin against thee.}

\latin{Bene\textbf{dí}ctus es, \textbf{Dó}\textbf{mi}ne:~* doce me justificatió\textit{nes} \textbf{tu}as.}\vern{Blessed art thou, O Lord: teach me thy justifications.}

\latin{In \textbf{lá}biis \textbf{me}is,~* pronuntiávi ómnia judícia o\textit{ris} \textbf{tu}i.}\vern{With my lips I have pronounced all the judgments of thy mouth.}

\latin{In via testimoniórum tuórum \textbf{de}le\textbf{ctá}\textbf{tus} sum,~* sicut in ómnibus \textit{di}\textbf{ví}tiis.}\vern{I have been delighted in the way of thy testimonies, as in all riches.}

\latin{In mandátis tuis \textbf{e}xer\textbf{cé}bor:~* et considerábo vi\textit{as} \textbf{tu}as.}\vern{I will meditate on thy commandments: and I will consider thy ways.}

\latin{In justificatiónibus tuis \textbf{me}di\textbf{tá}bor:~* non oblivíscar sermó\textit{nes} \textbf{tu}os.}\vern{I will think of thy justifications: I will not forget thy words.}

\latin{Glória \textbf{Pa}tri, et \textbf{Fí}\textbf{li}o,~* et Spirítu\textit{i} \textbf{San}cto.}\vern{}

\latin{Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per,~* et in sǽcula sæculó\textit{rum}. \textbf{A}men.}\vern{}

\subsubsection{Monday}

\psalm{23}

\gregorioscore{gabc/23-3b}

\setcounter{versecount}{2}
\latin{Quia ipse super mária fun\textbf{dá}vit \textbf{e}um:~* et super flúmina præpará\textit{vit} \textbf{e}um.}\vern{For he hath founded it upon the seas; and hath prepared it upon the rivers.}

\latin{Quis ascéndet in \textbf{mon}tem \textbf{Dó}\textbf{mi}ni?~* aut quis stabit in loco san\textit{cto} \textbf{e}jus?}\vern{Who shall ascend into the mountain of the Lord: or who shall stand in his holy place?}

\latin{Innocens mánibus et \textbf{mun}do \textbf{cor}de,~* qui non accépit in vano ánimam suam, nec jurávit in dolo próxi\textit{mo} \textbf{su}o.}\vern{The innocent in hands, and clean of heart, who hath not taken his soul in vain, nor sworn deceitfully to his neighbour.}

\latin{Hic accípiet benedicti\textbf{ó}nem a \textbf{Dó}\textbf{mi}no:~* et misericórdiam a Deo, salutá\textit{ri} \textbf{su}o.}\vern{He shall receive a blessing from the Lord, and mercy from God his Saviour.}

\latin{Hæc est generátio quæ\textbf{rén}tium \textbf{e}um,~* quæréntium fáciem De\textit{i} \textbf{Ja}cob.}\vern{This is the generation of them that seek him, of them that seek the face of the God of Jacob.}

\latin{Attóllite portas, príncipes, vestras,~† et elevámini, portæ \textbf{æ}ter\textbf{ná}les:~* et introíbit \textit{Rex} \textbf{gló}riæ.}\vern{Lift up your gates, O ye princes, and be ye lifted up, O eternal gates: and the King of Glory shall enter in.}

\latin{Quis est \textbf{i}ste Rex \textbf{gló}\textbf{ri}æ?~* Dóminus fortis et potens: Dóminus potens \textit{in} \textbf{prǽ}lio.}\vern{Who is this King of Glory? the Lord who is strong and mighty: the Lord mighty in battle.}

\latin{Attóllite portas, príncipes, vestras,~† et elevámini, portæ \textbf{æ}ter\textbf{ná}les:~* et introíbit \textit{Rex} \textbf{gló}riæ.}\vern{Lift up your gates, O ye princes, and be ye lifted up, O eternal gates: and the King of Glory shall enter in.}

\latin{Quis est \textbf{i}ste Rex \textbf{gló}\textbf{ri}æ?~* Dóminus virtútum ipse est \textit{Rex} \textbf{gló}riæ.}\vern{Who is this King of Glory? the Lord of hosts, he is the King of Glory.}

\latin{Glória \textbf{Pa}tri, et \textbf{Fí}\textbf{li}o,~* et Spirítu\textit{i} \textbf{San}cto.}\vern{}

\latin{Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per,~* et in sǽcula sæculó\textit{rum}. \textbf{A}men.}\vern{}

\subsection{Tuesday}

\psalm{24}

\gregorioscore{gabc/24-3b}

\setcounter{versecount}{2}
\latin{Neque irrídeant me ini\textbf{mí}ci \textbf{me}i:~* étenim univérsi, qui sústinent te, non con\textit{fun}\textbf{dén}tur.}\vern{Neither let my enemies laugh at me: for none of them that wait on thee shall be confounded.}

\latin{Confundántur omnes i\textbf{ní}qua a\textbf{gén}tes~* su\textit{per}\textbf{vá}cue.}\vern{Let all them be confounded that act unjust things without cause.}

\latin{Vias tuas, Dómine, de\textbf{món}stra \textbf{mi}hi~* et sémitas tuas é\textit{do}\textbf{ce} me.}\vern{Show, O Lord, thy ways to me, and teach me thy paths.}

\latin{Dírige me in veritáte \textbf{tu}a, et \textbf{do}\textbf{ce} me:~* quia tu es, Deus, Salvátor meus, et te sustínui to\textit{ta} \textbf{di}e.}\vern{Direct me in thy truth, and teach me; for thou art God my Saviour; and on thee have I waited all the day long.}

\latin{Reminíscere miseratiónum tu\textbf{á}rum, \textbf{Dó}\textbf{mi}ne,~* et misericordiárum tuárum, quia a sǽ\textit{cu}\textbf{lo} sunt.}\vern{Remember, O Lord, thy bowels of compassion; and thy mercies that are from the beginning of the world.}

\latin{Delícta juven\textbf{tú}tis \textbf{me}æ,~* et ignorántias meas ne \textit{me}\textbf{mí}neris.}\vern{The sins of my youth and my ignorances do not remember.}

\latin{Secúndum misericórdiam tuam me\textbf{mén}to \textbf{me}\textbf{i} tu,~* propter bonitátem tu\textit{am}, \textbf{Dó}mine.}\vern{According to thy mercy remember thou me: for thy goodness' sake, O Lord.}

\latin{Dulcis et \textbf{re}ctus \textbf{Dó}\textbf{mi}nus:~* propter hoc legem dabit delinquéntibus \textit{in} \textbf{vi}a.}\vern{The Lord is sweet and righteous: therefore he will give a law to sinners in the way.}

\latin{Díriget mansuétos \textbf{in} ju\textbf{dí}\textbf{ci}o:~* docébit mites vi\textit{as} \textbf{su}as.}\vern{He will guide the mild in judgment: he will teach the meek his ways.}

\latin{Univérsæ viæ Dómini, misericórdi\textbf{a} et \textbf{vé}\textbf{ri}tas,~* requiréntibus testaméntum ejus et testimóni\textit{a} \textbf{e}jus.}\vern{All the ways of the Lord are mercy and truth, to them that seek after his covenant and his testimonies.}

\latin{Propter nomen tuum, Dómine, propitiáberis pec\textbf{cá}to \textbf{me}o:~* multum \textit{est} \textbf{e}nim.}\vern{For thy name's sake, O Lord, thou wilt pardon my sin: for it is great.}

\latin{Quis est homo qui \textbf{ti}met \textbf{Dó}\textbf{mi}num?~* legem státuit ei in via, quam \textit{e}\textbf{lé}git.}\vern{Who is the man that feareth the Lord? He hath appointed him a law in the way he hath chosen.}

\latin{Anima ejus in bonis \textbf{de}mo\textbf{rá}\textbf{bi}tur:~* et semen ejus hereditá\textit{bit} \textbf{ter}ram.}\vern{His soul shall dwell in good things: and his seed shall inherit the land.}

\latin{Firmaméntum est Dóminus ti\textbf{mén}tibus \textbf{e}um:~* et testaméntum ipsíus ut manifesté\textit{tur} \textbf{il}lis.}\vern{The Lord is a firmament to them that fear him: and his covenant shall be made manifest to them.}

\latin{Oculi mei \textbf{sem}per ad \textbf{Dó}\textbf{mi}num:~* quóniam ipse evéllet de láqueo pe\textit{des} \textbf{me}os.}\vern{My eyes are ever towards the Lord: for he shall pluck my feet out of the snare.}

\latin{Réspice in me, et mise\textbf{ré}re \textbf{me}i:~* quia únicus et pauper \textit{sum} \textbf{e}go.}\vern{Look thou upon me, and have mercy on me; for I am alone and poor.}

\latin{Tribulatiónes cordis mei mul\textbf{ti}pli\textbf{cá}\textbf{tæ} sunt:~* de necessitátibus meis é\textit{ru}\textbf{e} me.}\vern{The troubles of my heart are multiplied: deliver me from my necessities.}

\latin{Vide humilitátem meam, et la\textbf{bó}rem \textbf{me}um:~* et dimítte univérsa delí\textit{cta} \textbf{me}a.}\vern{See my abjection and my labour; and forgive me all my sins.}

\latin{Réspice inimícos meos quóniam mul\textbf{ti}pli\textbf{cá}\textbf{ti} sunt:~* et ódio iníquo \textit{o}\textbf{dé}runt me.}\vern{Consider my enemies for they are multiplied, and have hated me with an unjust hatred.}

\latin{Custódi ánimam meam, et \textbf{é}ru\textbf{e} me:~* non erubéscam quóniam sperá\textit{vi} \textbf{in} te.}\vern{Keep thou my soul, and deliver me: I shall not be ashamed, for I have hoped in thee.}

\latin{Innocéntes et recti adhæ\textbf{sé}runt \textbf{mi}hi:~* quia sustí\textit{nu}\textbf{i} te.}\vern{The innocent and the upright have adhered to me: because I have waited on thee.}

\latin{Líbera, \textbf{De}us, \textbf{Is}\textbf{ra}ël:~* ex ómnibus tribulatióni\textit{bus} \textbf{su}is.}\vern{Deliver Israel, O God, from all his tribulations.}

\latin{Glória \textbf{Pa}tri, et \textbf{Fí}\textbf{li}o,~* et Spirítu\textit{i} \textbf{San}cto.}\vern{}

\latin{Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per,~* et in sǽcula sæculó\textit{rum}. \textbf{A}men.}\vern{}

\subsection{Wednesday}

\psalm{25}

\gregorioscore{gabc/25-3b}

\setcounter{versecount}{2}
\latin{Proba me, Dómi\textbf{ne}, et \textbf{ten}\textbf{ta} me:~* ure renes meos et \textit{cor} \textbf{me}um.}\vern{Prove me, O Lord, and try me; burn my reins and my heart.}

\latin{Quóniam misericórdia tua ante \textbf{ó}culos \textbf{me}\textbf{os} est:~* et complácui in veritá\textit{te} \textbf{tu}a.}\vern{For thy mercy is before my eyes; and I am well pleased with thy truth.}

\latin{Non sedi cum concílio \textbf{va}ni\textbf{tá}tis:~* et cum iníqua geréntibus non in\textit{tro}\textbf{í}bo.}\vern{I have not sat with the council of vanity: neither will I go in with the doers of unjust things.}

\latin{Odívi ecclésiam \textbf{ma}li\textbf{gnán}\textbf{ti}um:~* et cum ímpiis non \textit{se}\textbf{dé}bo.}\vern{I have hated the assembly of the malignant; and with the wicked I will not sit.}

\latin{Lavábo inter innocéntes \textbf{ma}nus \textbf{me}as:~* et circúmdabo altáre tu\textit{um}, \textbf{Dó}mine.}\vern{I will wash my hands among the innocent; and will compass thy altar, O Lord:}

\latin{Ut áudiam \textbf{vo}cem \textbf{lau}dis:~* et enárrem univérsa mirabíli\textit{a} \textbf{tu}a.}\vern{That I may hear the voice of thy praise: and tell of all thy wondrous works.}

\latin{Dómine, diléxi decórem \textbf{do}mus \textbf{tu}æ:~* et locum habitatiónis glóri\textit{æ} \textbf{tu}æ.}\vern{I have loved, O Lord, the beauty of thy house; and the place where thy glory dwelleth.}

\latin{Ne perdas cum ímpiis, Deus, \textbf{á}nimam \textbf{me}am,~* et cum viris sánguinum vi\textit{tam} \textbf{me}am.}\vern{Take not away my soul, O God, with the wicked: nor my life with bloody men:}

\latin{In quorum mánibus i\textbf{ni}qui\textbf{tá}\textbf{tes} sunt:~* déxtera eórum repléta est \textit{mu}\textbf{né}ribus.}\vern{In whose hands are iniquities: their right hand is filled with gifts.}

\latin{Ego autem in innocéntia \textbf{me}a in\textbf{grés}\textbf{sus} sum:~* rédime me, et miseré\textit{re} \textbf{me}i.}\vern{But as for me, I have walked in my innocence: redeem me, and have mercy on me.}

\latin{Pes meus stetit \textbf{in} di\textbf{ré}cto:~* in ecclésiis benedícam \textit{te}, \textbf{Dó}mine.}\vern{My foot hath stood in the direct way: in the churches I will bless thee, O Lord.}

\latin{Glória \textbf{Pa}tri, et \textbf{Fí}\textbf{li}o,~* et Spirítu\textit{i} \textbf{San}cto.}\vern{}

\latin{Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per,~* et in sǽcula sæculó\textit{rum}. \textbf{A}men.}\vern{}

\subsection{Thursday}

\psalm{22}

\gregorioscore{gabc/22-3b}

\setcounter{versecount}{2}
\latin{Super aquam refectiónis \textbf{e}du\textbf{cá}\textbf{vit} me:~* ánimam meam \textit{con}\textbf{vér}tit.}\vern{He hath brought me up, on the water of refreshment: He hath converted my soul.}

\latin{Dedúxit me super sémi\textbf{tas} ju\textbf{stí}\textbf{ti}æ:~* propter no\textit{men} \textbf{su}um.}\vern{He hath led me on the paths of justice, for his own name's sake.}

\latin{Nam, et si ambulávero in médio umbræ mortis, non ti\textbf{mé}bo \textbf{ma}la:~* quóniam \textit{tu} \textbf{me}cum es.}\vern{For though I should walk in the midst of the shadow of death, I will fear no evils, for thou art with me.}

\latin{Virga tua, et \textbf{bá}culus \textbf{tu}us:~* ipsa me con\textit{so}\textbf{lá}ta sunt.}\vern{Thy rod and thy staff, they have comforted me.}

\latin{Parásti in conspéctu \textbf{me}o \textbf{men}sam,~* advérsus eos, qui trí\textit{bu}\textbf{lant} me.}\vern{Thou hast prepared a table before me against them that afflict me.}

\latin{Impinguásti in óleo \textbf{ca}put \textbf{me}um:~* et calix meus inébrians quam \textit{præ}\textbf{clá}rus est!}\vern{Thou hast anointed my head with oil; and my chalice which inebriateth me, how goodly is it!}

\latin{Et misericórdia tua \textbf{sub}se\textbf{qué}\textbf{tur} me~* ómnibus diébus vi\textit{tæ} \textbf{me}æ.}\vern{And thy mercy will follow me all the days of my life.}

\latin{Et ut inhábitem in \textbf{do}mo \textbf{Dó}\textbf{mi}ni,~* in longitúdinem \textit{di}\textbf{é}rum.}\vern{And that I may dwell in the house of the Lord unto length of days.}

\latin{Glória \textbf{Pa}tri, et \textbf{Fí}\textbf{li}o,~* et Spirítu\textit{i} \textbf{San}cto.}\vern{}

\latin{Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per,~* et in sǽcula sæculó\textit{rum}. \textbf{A}men.}\vern{}

\subsection{Friday}

\psalm{83}

\gregorioscore{gabc/83-3b}

\setcounter{versecount}{2}
\latin{Cor meum, et \textbf{ca}ro \textbf{me}a:~* exsultavérunt in De\textit{um} \textbf{vi}vum.}\vern{My heart and my flesh have rejoiced in the living God.}

\latin{Etenim passer invénit \textbf{si}bi \textbf{do}mum:~* et turtur nidum sibi, ubi ponat pul\textit{los} \textbf{su}os.}\vern{For the sparrow hath found herself a house, and the turtle a nest for herself where she may lay her young ones:}

\latin{Altária tua, Dómi\textbf{ne} vir\textbf{tú}tum:~* Rex meus, et De\textit{us} \textbf{me}us.}\vern{Thy altars, O Lord of hosts, my king and my God.}

\latin{Beáti, qui hábitant in domo \textbf{tu}a, \textbf{Dó}\textbf{mi}ne:~* in sǽcula sæculórum \textit{lau}\textbf{dá}bunt te.}\vern{Blessed are they that dwell in thy house, O Lord: they shall praise thee for ever and ever.}

\latin{Beátus vir, cujus est auxílium abs te:~† ascensiónes in corde suo dispósuit, in valle \textbf{la}cri\textbf{má}rum~* in loco, \textit{quem} \textbf{pó}suit.}\vern{Blessed is the man whose help is from thee: in his heart he hath disposed to ascend by steps, In the vale of tears, in the place which be hath set.}

\latin{Etenim benedictiónem dabit legislátor~† ibunt de virtúte \textbf{in} vir\textbf{tú}tem:~* vidébitur Deus deórum \textit{in} \textbf{Si}on.}\vern{For the lawgiver shall give a blessing, they shall go from virtue to virtue: the God of gods shall be seen in Sion.}

\latin{Dómine, Deus virtútum, exáudi orati\textbf{ó}nem \textbf{me}am:~* áuribus pércipe, De\textit{us} \textbf{Ja}cob.}\vern{O Lord God of hosts, hear my prayer: give ear, O God of Jacob.}

\latin{Protéctor noster, \textbf{á}spice, \textbf{De}us:~* et réspice in fáciem Chri\textit{sti} \textbf{tu}i.}\vern{Behold, O God our protector: and look on the face of thy Christ.}

\latin{Quia mélior est dies una in \textbf{á}triis \textbf{tu}is:~* su\textit{per} \textbf{míl}lia.}\vern{For better is one day in thy courts above thousands.}

\latin{Elégi abjéctus esse in domo \textbf{De}i \textbf{me}i:~* magis quam habitáre in tabernáculis pec\textit{ca}\textbf{tó}rum.}\vern{I have chosen to be an abject in the house of my God, rather than to dwell in the tabernacles of sinners.}

\latin{Quia misericórdiam et veritátem \textbf{dí}ligit \textbf{De}us:~* grátiam et glóriam da\textit{bit} \textbf{Dó}minus.}\vern{For God loveth mercy and truth: the Lord will give grace and glory.}

\latin{Non privábit bonis eos qui ámbulant in \textbf{in}nocén\textbf{ti}a.~* Dómine virtútum, beátus homo qui spe\textit{rat} \textbf{in} te.}\vern{He will not deprive of good things them that walk in innocence: O Lord of hosts, blessed is the man that trusteth in thee.}

\latin{Glória \textbf{Pa}tri, et \textbf{Fí}\textbf{li}o,~* et Spirítu\textit{i} \textbf{San}cto.}\vern{}

\latin{Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per,~* et in sǽcula sæculó\textit{rum}. \textbf{A}men.}\vern{}

\subsection{Saturday}

\psalm{107}

\gregorioscore{gabc/107-3b}

\setcounter{versecount}{2}
\latin{Exsúrge, glória mea, exsúrge, psaltéri\textbf{um} et \textbf{cí}\textbf{tha}ra:~* exsúrgam \textit{di}\textbf{lú}culo.}\vern{Arise, my glory; arise, psaltery and harp: I will arise in the morning early.}

\latin{Confitébor tibi in \textbf{pó}pulis, \textbf{Dó}\textbf{mi}ne:~* et psallam tibi in na\textit{ti}\textbf{ó}nibus.}\vern{I will praise thee, O Lord, among the people: and I will sing unto thee among the populations.}

\latin{Quia magna est super cælos miseri\textbf{cór}dia \textbf{tu}a:~* et usque ad nubes véri\textit{tas} \textbf{tu}a:}\vern{For thy mercy is great above the heavens: and thy truth even unto the clouds.}

\latin{Exaltáre super cælos, Deus,~† et super omnem terram \textbf{gló}ria \textbf{tu}a:~* ut liberéntur dilé\textit{cti} \textbf{tu}i.}\vern{Be thou exalted, O God, above the heavens, and thy glory over all the earth: That thy beloved may be delivered.}

\latin{Salvum fac déxtera tua, \textbf{et} e\textbf{xáu}\textbf{di} me:~* Deus locútus est in san\textit{cto} \textbf{su}o:}\vern{Save with thy right hand and hear me. God hath spoken in his holiness.}

\latin{Exsultábo, et \textbf{dí}vidam \textbf{Sí}\textbf{chi}mam:~* et convállem tabernaculórum \textit{di}\textbf{mé}tiar.}\vern{I will rejoice, and I will divide Sichem and I will mete out the vale of tabernacles.}

\latin{Meus est Gálaad, et meus \textbf{est} Ma\textbf{nás}ses:~* et Ephraim suscéptio cápi\textit{tis} \textbf{me}i.}\vern{Galaad is mine, and Manasses is mine and Ephraim the protection of my head.}

\latin{\textbf{Ju}da rex \textbf{me}us:~* Moab lebes spe\textit{i} \textbf{me}æ.}\vern{Juda is my king: Moab the pot of my hope.}

\latin{In Idumǽam exténdam calcea\textbf{mén}tum \textbf{me}um:~* mihi alienígenæ amí\textit{ci} \textbf{fa}cti sunt.}\vern{Over Edom I will stretch out my shoe: the aliens are become my friends.}

\latin{Quis dedúcet me in civi\textbf{tá}tem mu\textbf{ní}tam?~* quis dedúcet me usque in I\textit{du}\textbf{mǽ}am?}\vern{Who will bring me into the strong city? who will lead me into Edom?}

\latin{Nonne tu, Deus, qui \textbf{re}pu\textbf{lí}\textbf{sti} nos,~* et non exíbis, Deus, in virtúti\textit{bus} \textbf{no}stris?}\vern{Wilt not thou, O God, who hast cast us off? and wilt not thou, O God, go forth with our armies?}

\latin{Da nobis auxílium de tribu\textbf{la}ti\textbf{ó}ne:~* quia vana sa\textit{lus} \textbf{hó}minis.}\vern{O grant us help from trouble: for vain is the help of man. }

\latin{In Deo faci\textbf{é}mus vir\textbf{tú}tem:~* et ipse ad níhilum dedúcet inimí\textit{cos} \textbf{no}stros.}\vern{Through God we shall do mightily: and he will bring our enemies to nothing.}

\latin{Glória \textbf{Pa}tri, et \textbf{Fí}\textbf{li}o,~* et Spirítu\textit{i} \textbf{San}cto.}\vern{}

\latin{Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per,~* et in sǽcula sæculó\textit{rum}. \textbf{A}men.}\vern{}

